Methods Power Study - Bimodal Simulations

### 2024-11-11 simulation_study/simulate_summary_bimodal.Rmd
update manuscript

```{r simulate-bimodal}
# simulate population 
normal_pops <- simulate_population(mu = 4, # item means
  mu_sigma = .2, # variability in item means 
  sigma = 2, # item standard deviations
  sigma_sigma = .2, # standard deviation of the standard deviations
  number_items = 30, # number of items
  number_scores = 1000, # number of participants
  smallest_sigma = .02, #* smallest possible standard deviation
  min_score = 1, #* minimum score for truncating purposes
  max_score = 7, #* maximum score for truncating purposes
  digits = 0) #* number of digits for rounding

floor_pops <- simulate_population(mu = 2, # item means
  mu_sigma = .2, # variability in item means 
  sigma = 1, # item standard deviations
  sigma_sigma = .1, # standard deviation of the standard deviations
  number_items = 30, # number of items
  number_scores = 1000, # number of participants
  smallest_sigma = .02, #* smallest possible standard deviation
  min_score = 1, #* minimum score for truncating purposes
  max_score = 7, #* maximum score for truncating purposes
  digits = 0) #* number of digits for rounding

ceiling_pops <- simulate_population(mu = 6, # item means
  mu_sigma = .2, # variability in item means 
  sigma = 1, # item standard deviations
  sigma_sigma = .1, # standard deviation of the standard deviations
  number_items = 30, # number of items
  number_scores = 1000, # number of participants
  smallest_sigma = .02, #* smallest possible standard deviation
  min_score = 1, #* minimum score for truncating purposes
  max_score = 7, #* maximum score for truncating purposes
  digits = 0) #* number of digits for rounding

# simulate sample 
item_number <- 1:30
prop_mix <- 1 # manipulated this number 
pilot_sample_size <- 30
bimodal_items <- sample(item_number, size = round(length(item_number)*prop_mix), replace = FALSE)

@@

>>>>

```{r simulate-bimodal}
# simulate population 
normal_pops <-semanticprimeR::simulate_population(mu = 4, # item means
  mu_sigma = .2, # variability in item means 
  sigma = 2, # item standard deviations
  sigma_sigma = .2, # standard deviation of the standard deviations
  number_items = 30, # number of items
  number_scores = 1000, # number of participants
  smallest_sigma = .02, #* smallest possible standard deviation
  min_score = 1, #* minimum score for truncating purposes
  max_score = 7, #* maximum score for truncating purposes
  digits = 0) #* number of digits for rounding

floor_pops <- semanticprimeR::simulate_population(mu = 2, # item means
  mu_sigma = .2, # variability in item means 
  sigma = 1, # item standard deviations
  sigma_sigma = .1, # standard deviation of the standard deviations
  number_items = 30, # number of items
  number_scores = 1000, # number of participants
  smallest_sigma = .02, #* smallest possible standard deviation
  min_score = 1, #* minimum score for truncating purposes
  max_score = 7, #* maximum score for truncating purposes
  digits = 0) #* number of digits for rounding

ceiling_pops <- semanticprimeR::simulate_population(mu = 6, # item means
  mu_sigma = .2, # variability in item means 
  sigma = 1, # item standard deviations
  sigma_sigma = .1, # standard deviation of the standard deviations
  number_items = 30, # number of items
  number_scores = 1000, # number of participants
  smallest_sigma = .02, #* smallest possible standard deviation
  min_score = 1, #* minimum score for truncating purposes
  max_score = 7, #* maximum score for truncating purposes
  digits = 0) #* number of digits for rounding

# simulate sample 
item_number <- 1:30
prop_mix <- .5 # manipulated this number 
pilot_sample_size <- 30
bimodal_items <- sample(item_number, size = round(length(item_number)*prop_mix), replace = FALSE)

@@

library(ggridges)

ggplot(researcher_sample %>% 
         filter(item < 11), aes(x = score, y = factor(item), fill = factor(item))) +
  geom_density_ridges(alpha = 0.7, scale = 1) +
  labs(x = "Score", y = "Item") +
  theme_minimal() +
  theme(legend.position = "none") + 
  coord_cartesian(xlim = c(1,7))
